Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
fix
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58608 72bbbca6-d526-0410-a7d9-f06f51895060
updates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58609 72bbbca6-d526-0410-a7d9-f06f51895060

 The syntactic structure of the original sentence is markedly spoken; the word \emph{seiska} is topicalised, and the main information ``deduced from phonotactics'' is in a subordinate clause. 
The translation into  is shorter and more precise, leaving just the main information.

@@

The statistical-machine translation approaches were implemented using the 
Moses toolkit \cite{koehn2007}. The training set up was that used for
the baseline system in the  in the WMT shared tasks
on machine translation.\footnote{\url{http://www.statmt.org/wmt11/baseline.html}}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Colloquial   & 45.31 & 71.28 & 11.95 \\
     Normalised   & 34.63 & 62.34 & 21.81 \\
     Standardised & 38.67 & 63.35 & 17.62 \\
     \hline
     rules-2      & 42.71 & 70.42 & 12.28 \\
     \hline
     cbmt-cn      & 44.44 & 74.17 & 12.35 \\
     pbmt-cn      & \textbf{38.38} & \textbf{66.81} & \textbf{17.90} \\
     \hline
  \end{tabular}
  \caption{Results for the translation task. The first three rows are the results 
    from translating the sections of the corpus. As with the }
  \label{table:results-trad}
\end{table}

>>>>

 The syntactic structure of the original sentence is markedly spoken; the word \emph{seiska} is topicalised, and the main information ``deduced from phonotactics'' is in a subordinate clause. 
The translation into standard Finnish is shorter and more precise, leaving just the main information.

@@

The statistical-machine translation approaches were implemented using the 
Moses toolkit \cite{koehn2007}. The training set up was that used for
the baseline system in the WMT shared tasks
on machine translation.\footnote{\url{http://www.statmt.org/wmt11/baseline.html}}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Colloquial   & 45.31 & 71.28 & 11.95 \\
     Normalised   & 34.63 & 62.34 & 21.81 \\
     Standardised & 38.67 & 63.35 & 17.62 \\
     \hline
     rules-2      & 42.71 & 70.42 & 12.28 \\
     \hline
     cbmt-cn      & 44.44 & 74.17 & 12.35 \\
     pbmt-cn      & \textbf{38.38} & \textbf{66.81} & \textbf{17.90} \\
     \hline
  \end{tabular}
  \caption{Results for the Finnish to English translation task. The first three rows are the results 
    from translating the sections of the corpus. As with the }
  \label{table:results-trad}
\end{table}
